A non-contextual hidden variable model for quantum mechanics

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

`contextuality'  is used to illustrate

@@

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. {\color{red} Our result
emphasises the importance of quantum dynamics
to the discussion of contextuality which may have
implications on our model and in general on the
notion of non-multiplicativity.}
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
%We expect this to provide new insights that will be useful
We expect {\color{red}our result} to provide new insights that will be useful
in the areas of foundations of QM and QIP.

>>>>

``contextuality''  is used to illustrate

@@

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. {\color{red} Our result
emphasises the importance of quantum dynamics
to the discussion of contextuality which so far is 
viewed merely as a kinematic phenomenon.}
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
%We expect this to provide new insights that will be useful
We expect {\color{red}our result} to provide new insights that will be useful
in the areas of foundations of QM and QIP.
